Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere

### 2020-06-06 doc/last/last.Rmd
readme

---
title: "Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere"
subtitle: "Running title: Sylvan Seeds, a forest germination database"
output: 
  bookdown::word_document2:
    reference_docx: gebtemplate.docx
bibliography: refs.bib
csl: global-ecology-and-biogeography.csl
link-citations: yes
always_allow_html: true
---

>>>>

---
title: "Sylvan Seeds, a database and web app to explore the seed germination ecology of temperate broadleaf and mixed forests of the northern hemisphere"
subtitle: "Running title: Sylvan Seeds, a forest germination database"
output: github_document
bibliography: refs.bib
csl: global-ecology-and-biogeography.csl
link-citations: yes
always_allow_html: true
---
